ntsIUTA Report Template

### 2022-11-29 dev/template_report.Rmd
LFU26 - updated msData peaks methods and tests

---
title: "ntsIUTA Report Template"
author: Ricardo Cunha
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    toc: yes
    toc_float: yes
    theme: paper
    code_folding: hide
    includes:
      in_header: !expr noquote(paste0(system.file(package = "streamFindData", dir = "extdata"), "\\logo_iuta_template_report.html"))
editor_options: 
  chunk_output_type: console
---

@@

knitr::opts_chunk$set(echo = TRUE, fig.align = "center", fig.width = 9, results = "asis")
path <- getwd()

```
<br> <br>

@@

The report was produced on `r Sys.time()`. The data and report are stored in ``r path`` of the workstation *`r Sys.info()["nodename"]`* under the user *`r Sys.info()["user"]`*.

@@

***
Insitut für Energie- und Umwelttechnik e.V. (IUTA)  
<br>
For further questions, please contact Ricardo Cunha ([cunha@iuta.de](cunha@iuta.de)).

>>>>

---
title: "ntsIUTA Report Template"
author:
  name: "Ricardo Cunha"
  affiliation: "Insitut für Energie- und Umwelttechnik e.V. (IUTA)"
  email: cunha@iuta.de
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    toc: yes
    toc_float: yes
    theme: paper
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

@@

path_extdata <- system.file(package = "streamFind", dir = "extdata")
logo <- file.path(path_extdata, "logo_iuta.png")

knitr::opts_chunk$set(echo = TRUE, fig.align = "center", fig.width = 9, results = "asis")

path_wd <- getwd()
```

```{r logo, echo=FALSE}
htmltools::img(
  src = knitr::image_uri(logo),
  alt = "logo",
  style =
    paste0("
      margin-left:inherit;
      position:absolute;
      top:60px;
      left:740px;
      width:", 100, "px;
      height:", 100*(216/207), "px;"
    )
)
```

@@

The report was produced on `r Sys.time()`. The data and report are stored in ``r path_wd`` of the workstation *`r Sys.info()["nodename"]`* under the user *`r Sys.info()["user"]`*.

@@

***
**Insitut für Energie- und Umwelttechnik e.V.**  
A: Bliersheimer Str. 58 - 60, 47229 Duisburg  
T: (02065) 418 - 0
